Formulating Regional Typologies

### 2023-11-01 regional_typologies.qmd
Update regional_typologies.qmd
updated collected data

-   Regions vary in socio-economic and environmental aspects.
-   Typologies simplify this by creating manageable groups.
-   They facilitate comparisons and targeted management.

@@

@@

|-----------------|-----------------|-----------------|----------------------|

@@

| **Typology** | **R.3.1 Establishment of Peatland Stewardship Village**                                                                                                                                                                                                               | **R.3.2 Enhancing Livelihood Capacity**                                                                                                          | **R.3.3 Development of Alternative Commodities and Livelihood Sources**                                                             |
|-----------------|-----------------|-----------------|----------------------|
| **1**        | \- Community awareness about the importance of the peat ecosystem, collaborating with district and provincial governments. <br><br> - Activities of the Peatland Stewardship Village aimed at increasing income and creating sources of livelihood for the community. | Conducted in synergy with district/city governments.                                                                                             | Directed at non-agricultural livelihood sources (off-farm). Local industries that exist need support.                               |
| **2**        | Peatland Stewardship Village is executed in an integrated manner in partnership with HTI companies and palm oil plantations. The goal is to enhance community access.                                                                                                 | Strengthening farmers' livelihoods to protect the remaining peat ecosystems. Formulation of alternative livelihood sources.                      | Livelihood sources oriented towards peat-friendly agriculture, mixed plantations combined with non-agricultural livelihood sources. |
| **3**        | Peatland Stewardship Village is oriented towards fire prevention; conducted in an integrated manner in partnership with HTI companies and palm oil plantations.                                                                                                       | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Livelihoods aimed at forest and land fire prevention. | Livelihood sources oriented towards peat-friendly agriculture and plantations combined with fisheries and livestock.                |
| **4**        | Peatland Stewardship Village geared towards fire prevention; enhancing community access to markets and high-economic value commodities.                                                                                                                               | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Emphasis on preventing forest and land fires.         | Livelihood sources focused on peat-friendly agriculture and plantations combined with fisheries and livestock.                      |
| **5**        | Peatland Stewardship Village focused on fire prevention; enhancing community access to markets and commodities of high economic value.                                                                                                                                | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Emphasis on preventing forest and land fires.         | Livelihood sources focused on peat-friendly agriculture and plantations combined with fisheries and livestock.                      |

>>>>

-   Regions vary in socio-economic and environmental aspects.
-   Typologies group regions with similar characteristics, making them more manageable.
-   They facilitate comparisons and targeted management.

@@

| No  | Data                                                    | Source                                                  | Unit           |
|------|---------------------------------|------------------------|------------------|
| 1   | Distance to plantation                                  | Land cover map 2020, MoEF                               | m              |
| 2   | Distance to road                                        | BIG                                                     | m              |
| 3   | Distance to commodity processing factory                | ICRAF (2016)                                            | m              |
| 4   | Distance to plantation concession                       | South Sulawesi Government                               | m              |
| 5   | Distance to forest                                      | Land cover map 2020, MoEF                               | m              |
| 6   | Distance to river                                       | BIG                                                     | m              |
| 7   | Distance to burned area                                 | MoEF, 2019                                              | m              |
| 8   | Percentage of agricultural area (small holder)          | Land cover map 2020, MoEF                               | \%             |
| 9   | Percentage of plantation area per sub-district          | Land cover map 2020, MoEF                               | \%             |
| 10  | Percentage of forested area in the sub-district         | Land cover map 2020, MoEF                               | \%             |
| 11  | Percentage of shrubland in the sub-district             | Land cover map 2020, MoEF                               | \%             |
| 12  | Percentage of water area compared to sub-district area  | Land cover map 2020, MoEF                               | \%             |
| 13  | Distance to deforestation                               | Land cover map 2020, MoEF                               | m              |
| 14  | Deforestation area size                                 | Land cover map 2020, MoEF                               | kmē            |
| 15  | Arable land (%)                                         | Land cover map 2020, MoEF                               | %/Sub district |
| 16  | Erosion                                                 | RUSLE                                                   | t ha?1 yr?1    |
| 17  | Flood hazard index                                      | RBI BNPB                                                | index value    |
| 18  | Land slide hazard index                                 | RBI BNPB                                                | index value    |
| 19  | Aridity index                                           | WORLDCLIM 2.1                                           | index value    |
| 20  | Total families based on electricity users and non-users | Potensi desa BPS 2019                                   | number         |
| 21  | Electrification ratio                                   | Potensi desa BPS 2019                                   | number         |
| 22  | High school ratio                                       | Potensi desa BPS 2019                                   | number         |
| 23  | University ratio                                        | Potensi desa BPS 2019                                   | number         |
| 24  | Hospital ratio                                          | Potensi desa BPS 2019                                   | number         |
| 25  | Health facility ratio                                   | Potensi desa BPS 2019                                   | number         |
| 26  | Market ratio                                            | Potensi desa BPS 2019                                   | number         |
| 27  | Minimarket ratio                                        | Potensi desa BPS 2019                                   | number         |
| 28  | Landslide events 2018-2019                              | Potensi desa BPS 2019                                   | events/year    |
| 29  | Landslide fatalities 2018-2019                          | Potensi desa BPS 2019                                   | people/year    |
| 30  | Flood events 2018-2019                                  | Potensi desa BPS 2019                                   | events/year    |
| 31  | Flood fatalities 2018-2019                              | Potensi desa BPS 2019                                   | people/year    |
| 32  | Flash flood events 2018-2019                            | Potensi desa BPS 2019                                   | events/year    |
| 33  | Flash flood fatalities 2018-2019                        | Potensi desa BPS 2019                                   | people/year    |
| 34  | Land and forest fire events 2018-2019                   | Potensi desa BPS 2019                                   | events/year    |
| 35  | Land and forest fire fatalities 2018-2019               | Potensi desa BPS 2019                                   | people/year    |
| 36  | Land drought events 2018-2019                           | Potensi desa BPS 2019                                   | events/year    |
| 37  | Land drought fatalities 2018-2019                       | Potensi desa BPS 2019                                   | people/year    |
| 38  | Natural disaster early warning systems                  | Potensi desa BPS 2019                                   | Number         |
| 39  | Percentage natural disaster early warning systems       | Potensi desa BPS 2019                                   | \%             |
| 40  | Reservoir ratio                                         | Potensi desa BPS 2019                                   | number         |
| 41  | Ratio of village markets                                | Potensi desa BPS 2019                                   | number         |
| 42  | Number of people suffering from malnutrition 2018       | Potensi desa BPS 2019                                   | number         |
| 43  | Ratio of people suffering from malnutrition 2018        | Potensi desa BPS 2019                                   | number         |
| 44  | Annual mean temperature                                 | WORLDCLIM 2.1                                           | 0 C            |
| 45  | Temperature changes                                     | WORLDCLIM 2.1                                           | 0 C            |
| 46  | Annual mean precipitation                               | WORLDCLIM 2.1                                           | mm             |
| 47  | Precipitation changes                                   | WORLDCLIM 2.1                                           | mm             |
| 48  | rasio_40pers_ekon_rendah_RT                             | National Team for the Acceleration of Poverty Reduction | number         |
| 49  | rasio_40pers_ekon_rendah_Indv                           | National Team for the Acceleration of Poverty Reduction | number         |
| 50  | Distance to irrigated land                              | Ministry of Public Works and Housing                    | m              |
| 51  | Percentage of irrigated land                            | Ministry of Public Works and Housing                    | ha             |
| 52  | Wet months                                              | WORLDCLIM 2.1                                           | months         |

@@

|-----------------|-----------------|-----------------|---------------------|

@@

| **Typology** | **R.3.1 Establishment of Peatland Stewardship Village**                                                                                                                                                                                                               | **R.3.2 Enhancing Livelihood Capacity**                                                                                                          | **R.3.3 Development of Alternative Commodities and Livelihood Sources**                                                             |
|-----------------|-----------------|-----------------|---------------------|
| **1**        | \- Community awareness about the importance of the peat ecosystem, collaborating with district and provincial governments. <br><br> - Activities of the Peatland Stewardship Village aimed at increasing income and creating sources of livelihood for the community. | Conducted in synergy with district/city governments.                                                                                             | Directed at non-agricultural livelihood sources (off-farm). Local industries that exist need support.                               |
| **2**        | Peatland Stewardship Village is executed in an integrated manner in partnership with HTI companies and palm oil plantations. The goal is to enhance community access.                                                                                                 | Strengthening farmers' livelihoods to protect the remaining peat ecosystems. Formulation of alternative livelihood sources.                      | Livelihood sources oriented towards peat-friendly agriculture, mixed plantations combined with non-agricultural livelihood sources. |
| **3**        | Peatland Stewardship Village is oriented towards fire prevention; conducted in an integrated manner in partnership with HTI companies and palm oil plantations.                                                                                                       | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Livelihoods aimed at forest and land fire prevention. | Livelihood sources oriented towards peat-friendly agriculture and plantations combined with fisheries and livestock.                |
| **4**        | Peatland Stewardship Village geared towards fire prevention; enhancing community access to markets and high-economic value commodities.                                                                                                                               | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Emphasis on preventing forest and land fires.         | Livelihood sources focused on peat-friendly agriculture and plantations combined with fisheries and livestock.                      |
| **5**        | Peatland Stewardship Village focused on fire prevention; enhancing community access to markets and commodities of high economic value.                                                                                                                                | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Emphasis on preventing forest and land fires.         | Livelihood sources focused on peat-friendly agriculture and plantations combined with fisheries and livestock.                      |
